\normalfont \normalsize \textsc{university, school or department name} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge Assignment Title \\ \horrule{2pt} \\[0.5cm]

### 2013-01-27 exercise3/paper/paper.tex

To run the application, execute the \texttt{kNN/run.sh} script. There is also a version for windows that was not tested.

@@

\begin{figure}[0.5\textwidth]
    \begin{center}
        \includegraphics[width=0.5\textwidth]{Skin_predicted_k5}
    \end{center}
    \caption['Skin-NonSkin' prediction with k=5]{The 'Skin-NonSkin' Data Set, colored by the predicted class attribute, with 5 neighbors as K parameter.}
    \label{fig:skin:predicted:k5}
\end{figure}

\begin{figure}[0.5\textwidth]
    \begin{center}
\includegraphics[width=0.5\textwidth]{Skin_correct_k5}
    \end{center}
\caption['Skin-NonSkin' correctness with k=5]{The 'Skin-NonSkin' Data Set, colored by correct or misclassified instance, with 5 neighbors as K parameter.}
\label{fig:skin:correct:k5}
\end{figure}

@@

\begin{figure}[0.5\textwidth]
    \begin{center}
\includegraphics[width=0.5\textwidth]{Skin_predicted_k100}
    \end{center}
\caption['Skin-NonSkin' prediction with k=100]{The 'Skin-NonSkin' Data Set, colored by the predicted class attribute, with 100 neighbors as K parameter.}
\label{fig:skin:predicted:k100}
\end{figure}

\begin{figure}[0.5\textwidth]
    \begin{center}
\includegraphics[width=0.5\textwidth]{Skin_correct_k100}
    \end{center}
\caption['Skin-NonSkin' correctness with k=100]{The 'Skin-NonSkin' Data Set, colored by correct or misclassified instance, with 100 neighbors as K parameter.}
\label{fig:skin:correct:k100}
\end{figure}

We observe a similar result for the truncated 'Iris' data set. K-NN works very well except for some instances on the boundaries, figure \ref{fig:iris:correct:k5} shows us misclassfied instances exactly on the hyperplane between 'Iris versicolor' and 'Iris virginica'. The predicted instances can be seen in figure \ref{fig:iris:predicted:k5}.
\begin{figure}[0.5\textwidth]
    \begin{center}
\includegraphics[width=0.5\textwidth]{Iris_predicted_k5}
    \end{center}
\caption['Iris' prediction with k=5]{The 'Iris' Data Set, colored by the predicted class attribute, with 5 neighbors as K parameter.}
\label{fig:iris:predicted:k5}
\end{figure}

\begin{figure}[0.5\textwidth]
    \begin{center}
\includegraphics[width=0.5\textwidth]{Iris_correct_k5}
    \end{center}
\caption['Iris' correctness with k=5]{The 'Iris' Data Set, colored by correct or misclassified instance, with 5 neighbors as K parameter.}
\label{fig:iris:correct:k5}
\end{figure}

Unlike the two previous data sets, the 'Haberman' data set does not contain clearly separable spaces where one of the class values dominates. Accordingly, the K-NN algorithm performs rather poor on this input set. Figure \ref{fig:haberman:correct:k13} shows the best distribution of correct and misclassified instances, namely 31 misclassified and 131 correctly classfied instances. It is notably that a k parameter of 13 is a rather high value. This fact could be interpreted in a sense that low k-values are preferable in case of easily separable data sets and higher k-values should be used for more overlapping, more scattered data sets.
\begin{figure}[0.5\textwidth]
    \begin{center}
\includegraphics[width=0.5\textwidth]{Haberman_correct_k13}
    \end{center}
\caption['Haberman' correctness with k=13]{The 'Haberman' Data Set, colored by correct or misclassified instance, with 13 neighbors as K parameter.}
\label{fig:haberman:correct:k13}
\end{figure}
\end{document}

>>>>

To run the application, execute the \texttt{knn-java-gui/run.sh} script. There is also a script to compile the source \texttt{knn-java-gui/compile.sh}. Both scripts also have versions for windows.

@@

\begin{figure}[\textwidth]
    \begin{center}
        \includegraphics[width=\textwidth]{Skin_predicted_k5}
    \end{center}
    \caption['Skin-NonSkin' prediction with k=5]{The 'Skin-NonSkin' Data Set, colored by the predicted class attribute, with 5 neighbors as K parameter.}
    \label{fig:skin:predicted:k5}
\end{figure}

\begin{figure}[\textwidth]
    \begin{center}
\includegraphics[width=\textwidth]{Skin_correct_k5}
    \end{center}
\caption['Skin-NonSkin' correctness with k=5]{The 'Skin-NonSkin' Data Set, colored by correct or misclassified instance, with 5 neighbors as K parameter.}
\label{fig:skin:correct:k5}
\end{figure}

@@

\begin{figure}[\textwidth]
    \begin{center}
\includegraphics[width=\textwidth]{Skin_predicted_k100}
    \end{center}
\caption['Skin-NonSkin' prediction with k=100]{The 'Skin-NonSkin' Data Set, colored by the predicted class attribute, with 100 neighbors as K parameter.}
\label{fig:skin:predicted:k100}
\end{figure}

\begin{figure}[\textwidth]
    \begin{center}
\includegraphics[width=\textwidth]{Skin_correct_k100}
    \end{center}
\caption['Skin-NonSkin' correctness with k=100]{The 'Skin-NonSkin' Data Set, colored by correct or misclassified instance, with 100 neighbors as K parameter.}
\label{fig:skin:correct:k100}
\end{figure}

We observe a similar result for the truncated 'Iris' data set. K-NN works very well except for some instances on the boundaries, figure \ref{fig:iris:correct:k5} shows us misclassfied instances exactly on the hyperplane between 'Iris versicolor' and 'Iris virginica'. The predicted instances can be seen in figure \ref{fig:iris:predicted:k5}.
\begin{figure}[\textwidth]
    \begin{center}
\includegraphics[width=\textwidth]{Iris_predicted_k5}
    \end{center}
\caption['Iris' prediction with k=5]{The 'Iris' Data Set, colored by the predicted class attribute, with 5 neighbors as K parameter.}
\label{fig:iris:predicted:k5}
\end{figure}

\begin{figure}[\textwidth]
    \begin{center}
\includegraphics[width=\textwidth]{Iris_correct_k5}
    \end{center}
\caption['Iris' correctness with k=5]{The 'Iris' Data Set, colored by correct or misclassified instance, with 5 neighbors as K parameter.}
\label{fig:iris:correct:k5}
\end{figure}

Unlike the two previous data sets, the 'Haberman' data set does not contain clearly separable spaces where one of the class values dominates. Accordingly, the K-NN algorithm performs rather poor on this input set. Figure \ref{fig:haberman:correct:k13} shows the best distribution of correct and misclassified instances, namely 31 misclassified and 131 correctly classfied instances. It is notably that a k parameter of 13 is a rather high value. This fact could be interpreted in a sense that low k-values are preferable in case of easily separable data sets and higher k-values should be used for more overlapping, more scattered data sets.
\begin{figure}[\textwidth]
    \begin{center}
\includegraphics[width=\textwidth]{Haberman_correct_k13}
    \end{center}
\caption['Haberman' correctness with k=13]{The 'Haberman' Data Set, colored by correct or misclassified instance, with 13 neighbors as K parameter.}
\label{fig:haberman:correct:k13}
\end{figure}
\end{document}
